---
title: "Test Vignette"
---

```{r setup}
knitr::opts_chunk$set(
  eval = identical(Sys.getenv("NOT_CRAN"), "true")
)
```

This is a testing vignette to make sure the conditional evaluation works.

```{r}
print("Starting expensive computation")
Sys.sleep(5)
print("Done!")
```

Above should print two lines.

## "Likelihood" from [`rstanarm`](https://mc-stan.org/rstanarm/articles/lm#likelihood)

The likelihood for one observation under a linear model can be written as a
conditionally normal PDF
$$\frac{1}{\sigma_{\epsilon} \sqrt{2 \pi}} 
  e^{-\frac{1}{2} \left(\frac{y - \mu}{\sigma_{\epsilon}}\right)^2},$$
where $\mu = \alpha + \mathbf{x}^\top \boldsymbol{\beta}$ is a linear predictor
and $\sigma_{\epsilon}$ is the standard deviation of the error in predicting
the outcome, $y$. The likelihood of the entire sample is the product of $N$
individual likelihood contributions.

It is well-known that the likelihood of the sample is maximized when the 
sum-of-squared residuals is minimized, which occurs when
$$ \widehat{\boldsymbol{\beta}} = \left(\mathbf{X}^\top \mathbf{X}\right)^{-1}
                                   \mathbf{X}^\top \mathbf{y}, $$
$$ \widehat{\alpha} = \overline{y} - \overline{\mathbf{x}}^\top 
                                     \widehat{\boldsymbol{\beta}}, $$
$$ \widehat{\sigma}_{\epsilon}^2 = 
  \frac{\left(\mathbf{y} - \widehat{\alpha} - \mathbf{X} \widehat{
                                              \boldsymbol{\beta}}\right)^\top
        \left(\mathbf{y} - \widehat{\alpha} - \mathbf{X} \widehat{
                                              \boldsymbol{\beta}}\right)}{N},$$
where $\overline{\mathbf{x}}$ is a vector that contains the sample means of the
$K$ predictors, $\mathbf{X}$ is a $N \times K$ matrix of _centered_ predictors, 
$\mathbf{y}$ is a $N$-vector of outcomes and $\overline{y}$ is the sample mean 
of the outcome.

Boldsymbol should render, i.e. this should render properly: $\boldsymbol{\beta}$ vs $\beta$ and not error out.
